---
title: "Shit I Need to Do"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: united
---

```{r setup, include=FALSE}
library(dplyr)
#library(flexdashboard)
library(ggraph)
library(ggplot2)
library(googlesheets4)
#library(hrbrthemes)
library(igraph)
library(kableExtra)
library(tidyverse)
library(tidytext)
library(viridis)
library(wesanderson)


# set most recent month and year
current_month <- "Jul"
current_year <- "2021"


# import the kraken 
task_list <- read_sheet("google_sheets_url_here")


# add columns for month because we might want them
task_list <- task_list %>%
  add_column(Month_Due = NA, Month_Complete = NA, Full_Due_Date = NA) %>%
  mutate(Month_Due = Due_Date, Month_Complete = Complete_Date, Full_Due_Date = Due_Date) %>%
  add_column(Year_Due = NA, Year_Complete = NA) %>%
  mutate(Year_Due = Due_Date, Year_Complete = Complete_Date) %>%
  mutate(
    Month_Due = as.factor(Month_Due),
    Year_Due = as.factor(Year_Due), 
    Month_Due = as.factor(Month_Due),
    Month_Complete = as.factor(Month_Complete)
  )


# tidy it 
task_list$Due_Date <- substr(task_list$Due_Date, 6, 10)

task_list$Month_Due <- substr(task_list$Month_Due, 6, 7)
task_list$Month_Complete <- substr(task_list$Month_Complete, 6, 7)

task_list$Year_Due <- substr(task_list$Year_Due, 1, 4)
task_list$Year_Complete <- substr(task_list$Year_Complete, 1, 4)


# order it --> month due
task_list <- task_list %>%
  mutate(Month_Due = ifelse(Month_Due == "01", "Jan", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "02", "Feb", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "03", "Mar", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "04", "Apr", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "05", "May", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "06", "Jun", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "07", "Jul", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "08", "Aug", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "09", "Sep", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "10", "Oct", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "11", "Nov", Month_Due)) %>%
  mutate(Month_Due = ifelse(Month_Due == "12", "Dec", Month_Due))

task_list$Month_Due <- ordered(task_list$Month_Due, 
                     levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep",
                              "Oct", "Nov", "Dec"))


# order it --> month complete
task_list <- task_list %>%
  mutate(Month_Complete = ifelse(Month_Complete == "01", "Jan", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "02", "Feb", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "03", "Mar", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "04", "Apr", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "05", "May", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "06", "Jun", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "07", "Jul", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "08", "Aug", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "09", "Sep", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "10", "Oct", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "11", "Nov", Month_Complete)) %>%
  mutate(Month_Complete = ifelse(Month_Complete == "12", "Dec", Month_Complete))

task_list$Month_Complete <- ordered(task_list$Month_Complete, 
                     levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep",
                              "Oct", "Nov", "Dec"))


```

Overall Things to Do {data-navmenu="Overview"}
=====================================

Column
-----------------------------------------------------------------------

### All the Shit I Have to Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
task_list %>%
  filter(Complete == "No") %>%
  select(c(Work_Area, Project, Task, Due_Date)) %>%
  rename(`Work Area` = Work_Area, `Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(4, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Things Needing to be Done - Personal

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
task_list %>%
  filter(Month_Due == current_month) %>%
  filter(Complete == "No") %>%
  filter((Life_Area == "Personal")) %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  rename(`Due Date` = Due_Date) %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")
  

```

### Things Needing to be Done - PhD Life and Moving

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
task_list %>%
  filter(Month_Due == current_month) %>%
  filter(Complete == "No") %>%
  filter((Life_Area == "Inverted Diaspora") | (Life_Area == "PhD Life")) %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")

```

### Things Needing to be Done - RHINO and Other Profesh Things

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Month_Due == current_month) %>%
  filter(Complete == "No") %>%
  filter((Life_Area == "RHINO") | (Life_Area == "Professional Associations") | (Life_Area == "Professional Development")) %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  rename(`Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")

```

### Things Needing to be Done - Teaching

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Month_Due == current_month) %>%
  filter(Complete == "No") %>%
  filter((Life_Area == "Teaching")) %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  rename(`Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")

```

Overview {data-navmenu="Personal"}
=====================================

Column
-----------------------------------------------------------------------

### Personal - To Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "No") %>%
  filter(Life_Area == "Personal") %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Done - Household

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Personal") %>%
  filter(Work_Area == "Household") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - Parenting

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Personal") %>%
  filter(Work_Area == "Parenting") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - Everything Else

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Personal") %>%
  filter((Work_Area != "Household") | (Work_Area != "Parenting")) %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

General RHINO {data-navmenu="RHINO"}
=====================================

Column
-----------------------------------------------------------------------

### General RHINO - To Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "No") %>%
  filter(Life_Area == "RHINO") %>%
  filter((Work_Area != "RHINO Community of Practice") & (Work_Area != "ED-SNSRO") & (Work_Area != "FASTER") & (Work_Area != "OD2A") & 
           (Work_Area != "WTSC")) %>%
  select(c(Work_Area, Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Work Area` = Work_Area, `Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(4, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Done - Administrative

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "RHINO") %>%
  filter(Work_Area == "Administrative") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - Surveillance

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "RHINO") %>%
  filter((Work_Area != "RHINO Community of Practice") & (Work_Area != "ED-SNSRO") & (Work_Area != "FASTER") & 
           (Work_Area != "OD2A") & (Work_Area != "WTSC") & (Work_Area != "Administrative") & 
           (Work_Area != "Race and Ethnicity Data Project") & 
           (Work_Area != "User Support") & (Work_Area != "Tyler Practicum")) %>%
  group_by(Work_Area, Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Work Area` = Work_Area, `Tasks Completed` = "sum(n)", 
         `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em") %>%
  column_spec(5, width = "7em")

```

### Done - Student Projects

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "RHINO") %>%
  filter((Work_Area == "Race and Ethnicity Data Project") | (Project == "W34 Investigation") | (Work_Area == "Shafaq Practicum") | 
           (Work_Area == "Margaret Practicum")) %>%
  group_by(Work_Area, Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Work Area` = Work_Area, `Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em") %>%
  column_spec(5, width = "7em")

```

Community of Practice {data-navmenu="RHINO"}
=====================================

Column
-----------------------------------------------------------------------

### RHINO Community of Practice - To Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "No") %>%
  filter(Work_Area == "RHINO Community of Practice") %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Done - Community of Practice Calls

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Work_Area == "RHINO Community of Practice") %>%
  filter(Project == "Community of Practice Call") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - ESSENCE Skills Training

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Work_Area == "RHINO Community of Practice") %>%
  filter(Project == "ESSENCE Skills Webinars") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - User Support

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Work_Area == "RHINO Community of Practice") %>%
  filter((Project == "Publication Review") | (Project == "User Support")) %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

Grants {data-navmenu="RHINO"}
=====================================

Column
-----------------------------------------------------------------------

### To Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "No") %>%
  filter(Life_Area == "RHINO") %>%
  filter((Work_Area == "FASTER") | (Work_Area == "ED-SNSRO") | (Work_Area == "OD2A") | (Work_Area == "WTSC")) %>%
  select(c(Work_Area, Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Work Area` = Work_Area, `Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(4, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Done - ED-SNSRO

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "RHINO") %>%
  filter(Work_Area == "ED-SNSRO") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - FASTER

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "RHINO") %>%
  filter(Work_Area == "FASTER") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - OD2A

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "RHINO") %>%
  filter(Work_Area == "OD2A") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - WTSC

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "RHINO") %>%
  filter(Work_Area == "WTSC") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

Overview {data-navmenu="PhD Life"}
=====================================

Column
-----------------------------------------------------------------------

### PhD Life - To Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "No") %>%
  filter((Life_Area == "PhD Life") | (Life_Area == "Inverted Diaspora")) %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Done - Thesis

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "PhD Life") %>%
  filter(Work_Area == "Thesis") %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")


```

### Done - Inverted Diaspora

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Inverted Diaspora") %>%
  group_by(Work_Area, Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Work Area` = Work_Area, `Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em") %>%
  column_spec(5, width = "7em")

```

### Done - Everything Else

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "PhD Life") %>%
  filter(Project != "Thesis") %>%
  group_by(Work_Area, Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Work Area` = Work_Area, `Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em") %>%
  column_spec(5, width = "7em")

```

UW Struggle Bus {data-navmenu="Teaching"}
=====================================

Column
-----------------------------------------------------------------------

### Teaching - To Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "No") %>%
  filter((Life_Area == "Teaching")) %>%
  select(c(Work_Area, Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Work Area` = Work_Area, `Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(4, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Done - UW Bothell

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Teaching") %>%
  filter((Work_Area == "UW Bothell") | (Work_Area == "BHLTH 201") | (Work_Area == "BHLTH 301")  | 
           (Work_Area == "BHS 201")) %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - UW School of Public Health

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Teaching") %>%
  filter((Work_Area == "UW SPH Health Services") | (Work_Area == "UW SPH Epidemiology")) %>%
  group_by(Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em")

```

### Done - Everything Else

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Teaching") %>%
  filter((Work_Area != "UW SPH Health Services") & (Work_Area != "UW Bothell") & (Work_Area != "BHLTH 201") 
         & (Work_Area != "BHLTH 301")  & (Work_Area != "BHS 201")) %>%
  group_by(Work_Area, Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Work Area` = Work_Area, `Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, 
         `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em") %>%
  column_spec(5, width = "7em")

```

Other Professional Things {data-navmenu="Other Professional"}
=====================================

Column
-----------------------------------------------------------------------

### Other Professional Things - To Do

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "No") %>%
  filter((Life_Area == "Professional Development") | (Life_Area == "Professional Associations")) %>%
  select(c(Project, Task, Due_Date, Notes)) %>%
  arrange(Due_Date) %>%
  rename(`Due Date` = Due_Date) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed"))  %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "4em", background = "yellow")

```

Column
-----------------------------------------------------------------------

### Done - Professional Associations

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Professional Associations") %>%
  group_by(Work_Area, Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Work Area` = Work_Area, `Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, 
         `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em") %>%
  column_spec(5, width = "7em")

```

### Done - Professional Development

```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

task_list %>%
  filter(Complete == "Yes") %>%
  filter(Life_Area == "Professional Development") %>%
  group_by(Work_Area, Project, Year_Complete, Month_Complete) %>%
  count(Task) %>%
  summarise(sum(n)) %>%
  rename(`Work Area` = Work_Area, `Tasks Completed` = "sum(n)", `Year Complete` = Year_Complete, `Month Complete` = Month_Complete) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "7em") %>%
  column_spec(5, width = "7em")

```
